Evaluation of performances

### 2020-04-30 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (%)", RMSE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Percentage of selected features of each fold during optimization for selected learners",
    label = "tab:tune-perc-sel-features"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )
```

@@

```{r}
getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::summarise(
    "Mean (Features (%))" = mean(`Features (%)`),
    "SD (Features (%))" = sd(`Features (%)`)
  )
```

>>>>

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (\\%)", RMSE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Percentage of selected features of each fold during optimization for selected learners",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 2)
  )

table4 %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = FALSE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    booktabs = TRUE,
    # important to treat content of multirow as latex content
    sanitize.text.function = force
  )

saveRDS(table4, here("docs/00-manuscripts/presentation/tune-perc-sel-feature.rda"))

table4 %>%
  flextable() %>%
  autofit()
```

@@

```{r}
getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::summarise(
    "Mean (Features (%))" = mean(`Features (%)`),
    "SD (Features (%))" = sd(`Features (%)`)
  ) %>% 
  flextable() %>% 
  autofit()
```
